\LARGE Coursework \\ Module Name (CMM536)

### 2018-04-27 submission_bak.tex
graphics added

The paper that was chosen for this work is \cite{Liu:2017:ERI:3097983.3098049}. The authors attempted to improve methods for classifying encrypted messaging traffic through streaming methods. Below is a review of this paper that includes problem statement, related work and methods applied.\\

\subsection{Problem Statement}

@@

\subsection{Relevant Work}
The paper acknowleges previous studies \emph{Haffner:2005:AAC:1080173.1080183} \cite{4669733}  \emph{1550864} which were able to classify messaging data through the port number, protocol signature and protocol type. However, these methods are not applicable for encrypted data. Later studies \cite{5693957}, including one by the same team \cite{7377112}, were able to classify encrypted data using machine learning by segmenting traffic and then classifying it. These attempts suffered from low relative accuracy and speed.

@@

@@

Now the model is incrementally trained and tested by feeding in chunks sequentially. For each iteration a training chunk is presented and the model is incrementally trained on that chunk. Then a testing chunk is presented to assess the performance of the model for each iteration, printing the current accuracy to the console. \textit{Full output not included in this document for brevity}.

\begin{Schunk}
\begin{Sinput}
>#train over the stream
>for (i in 1:turns){
>  # next sample
> sample <- dfStream$get_points(dfStream, n = chunk,
+                               outofpoints = c("stop", "warn", "ignore"))
>  test_sample <- test_stream$get_points(test_stream, n = test_chunk,
+                                       outofpoints = c("stop", "warn", "ignore"))
>  ## Update the trained model with the new chunks
>  myboostedclassifier <- trainMOA(model = myboostedclassifier$model,
+                                  formula = won ~ .,
+                                  data = datastream_dataframe(sample),
+                                  reset = FALSE,trace = FALSE)
>  cat("chunk: ",i,"\n")

>  predictions <- predict(myboostedclassifier, test_sample)
>  # calculate accuracy
>  accuracies[i] <- sum(predictions==test_sample$won)/nrow(test_sample)*100
>  if(i %% 100 = 0){
>  cat("chunk ",i," accuracy = ",accuracies[i],"%","\n")
>  }
>}

\end{Sinput}
\end{Schunk}

The final accuracy achieved was 58.1\%, which is actually higher than for the best non-streaming model. This may be due to the use of a different model type which performed better on the given dataset. This is also a reasonably high accuracy for this problem - as stated earlier, anything above 50\% is considered a positive result since an ideal game should be perfectly balanced.

The improvement in accuracy with training/testing iteration is plotted below. We see that the classifier was rather erratic in accuracy as more data was presented to it. The general trend was for accuracy to steadily increase, although peak accuracy was reached aroumd chunk 350, suggesting only about half the data was required to fit a model. However, accuracy was increasing towards the end of the streaming process, so a larger dataset may have given even better results.

\begin{Schunk}
\begin{Sinput}
>accuracies <- as.data.frame(accuracies)
>ggplot(accuracies,aes(y=accuracies,x=seq(1,length(accuracies))))+
+  geom_line(col="blue",alpha=0.7)+
+ geom_smooth(method="lm",col="red")+
+  labs(title="accuracy of streaming classifier",subtitle="trendline shown in red")+
+  xlab("chunk")+
+  ylab("accuracy")

\end{Sinput}
\end{Schunk}

\begin{figure}[H]
\begin{center}
\includegraphics{stream_result}
\caption {Progressive accuracy of the stream classifier}
\label{fig2}
\end {center}
\end {figure}

>>>>

[your text goes here]
The paper that was chosen for this work is \cite{6779381}. The authors provided a full review on different streaming algorithms and methos that handle concept drfit?. Below is a review of this paper that includes problem statement, related work and methods applied.\\

\textcolor{blue}{\textit{Notice how I cited the paper, and how does it appear in the document, to do so, you need to have a file in your working director (references.bib), this file simply contains the bibtext items for the papers you chose. These BibTex items are often avaiable to download from publishers website, see Figure~\ref{fig1}}}
\subsection{Problem Statement}

@@

\subsection{Relevant Work}
The paper acknowleges previous studies \emph{Haffner2005} \emph{Raahemi2008}  \emph{Zander2005} which were able to classify messaging data through the port number, protocol signature and protocol type. However, these methods are not applicable for encrypted data. Later studies \emph{Huanhuan2005} \emph{Fu2016}, including one by the same team \emph{Fu2016}, were able to classify encrypted data using machine learning by segmenting traffic and then classifying it. These attempts suffered from low relative accuracy and speed.

@@

-TODO citations

@@
